Plausibility Norming

### 2024-06-11 code_data/plausibility_norming/plausibility_report_HighvsLowSem.Rmd
edits to plausibility code

@@

@@

df %>% group_by(condition) %>%
             dplyr::summarize(mean_rating = mean(value, na.rm=TRUE), 
                              sd_rating = sd(value, na.rm=TRUE))

@@

test_wider <- test %>% pivot_wider(names_from = condition, values_from = mean_rating)

t.test(test_wider$c, test_wider$d, paired=TRUE)

@@

# raw plausibility rating as predictor
m_plausib <- lmer(log(rt) ~ mean_rating +
                       (1 |fullname)+  
                       (1 |item), 
                     data=precrit_plausib, REML=FALSE)

summary(m_plausib)

>>>>

head(df)

@@

## SV: isn't this simpler than your obscure code above?
length(unique(df$md5_hash_participant_IP))

colnames(df)

@@

## SV: this calculation is incorrect as it is not aggregated first:
df %>% group_by(condition) %>%
             dplyr::summarize(mean_rating = mean(value, na.rm=TRUE), 
                              sd_rating = sd(value, na.rm=TRUE))

@@

## SV: redone so I can understand it
xtabs(~subject+condition,df_crit)

df_crit<-subset(df,condition!="f")

xtabs(~subject+condition,df_crit)

xtabs(~item+condition,df_crit)

## c is low, d is high int:
df_crit$cond<-ifelse(df_crit$condition=="c",0.5,-0.5)

library(lme4)
m<-lmer(value~cond + (1+cond|subject) + (1+cond|item),df_crit)
## low semantic int conditions are more plausible than high:
summary(m)
library(car)
## normal approximation seems OK:
qqPlot(residuals(m))

## looks OK:
acf(residuals(m))

## SV: why are we doing this t-test at all?
test_wider <- test %>% pivot_wider(names_from = condition, values_from = mean_rating)

head(test_wider)

## SV: You can see that this t-test is over-enthusiastic because it
## hides significant by-item variance by averaging it away (see the lmer
## results above--by item variability is remarkably high)
t.test(test_wider$c, test_wider$d, paired=TRUE)

@@

# raw plausibility rating as predictor
library(MASS)
m_lm<-lm(rt~mean_rating,precrit_plausib)

m_plausib <- lmer(log(rt) ~ mean_rating +
                       (1 |fullname)+  
                       (1 |item), 
                     data=precrit_plausib, REML=FALSE)
```

```{r}
summary(m_plausib)
## strong skew:
qqPlot(residuals(m_plausib)
### massive autocorrelation:       
acf(residuals(m_plausib))

m_plausib <- lmer(log(rt) ~ scale(mean_rating,scale=FALSE) +
                       (1 + scale(mean_rating,scale=FALSE)|fullname)+  
                       (1 + scale(mean_rating,scale=FALSE)|item), 
                     data=precrit_plausib, REML=FALSE)

summary(m_plausib)
### massive autocorrelation remains. Why?       
acf(residuals(m_plausib))
```

SV: here, instead of fitting to mean ratings only, can you store the mean by-item ratings as well as the SE in the data frame used for the inner join above? Then center the mean ratings. 
So, the data frame used in the model m_plausib should then have not just the centered mean_rating but also the SE. Then the measurement error model would be (possible in brms only):

```
mbrms<-brm(formula = rt ~ me(c_mean_rating, se_mean_rating) +
(1 | fullname) + (1|item),
data = precrit_plausib, family = lognormal(), prior = some_uninf_priors,
iter = 2000, chains = 4,
control = list(adapt_delta = 0.999,
max_treedepth = 15))
```

SV: Then use the measurement error syntax in the model below where you compare sem with ratings.
